\section{ALGORITHMS}
Following the notation in section \ref{sec:model}, we introduce the Expectation Maximization (EM) algorithms for estimating $w$ with robustified objective function to learn the mobility of landmarks and estimate the robot trajectory and the map.

\subsection{Estimation of Latent Parameters}
\label{sec:traditionalEM}

As described in \cite{rogers2010slam}, in Equation \ref{eq:sensor}, the hidden variables $w_k$ must be estimated from multiple observations of each landmark. In the \textbf{M step}, we select the optimal $\boldsymbol{w}$ which maximizes the joint likelihood. However there is a trivial solution to the likelihood maximization which sets $w_k = 0$ for all $k$, we penalize the log-likelihood objective in Equation \ref{eq:lagrangeMultiplier} with Lagrange multiplier which act as priors of the latent landmark mobility variables:
\begin{multline}
%\begin{aligned}
\mathrm{Obj}(Z, X, L, W) = \\ \sum_k \left[ -w_{j_k}(\tilde{\boldsymbol{\mu}}^T_k\boldsymbol{\Sigma}_k^{-1}\tilde{\boldsymbol{\mu}}_k) \right] - \frac{1}{2}\lambda(1 - \boldsymbol{w})^T(1 - \boldsymbol{w})
%\end{aligned}
\label{eq:lagrangeMultiplier}
\end{multline}
where $\tilde{\boldsymbol{\mu}}_k = v_k (h_k(\boldsymbol{x}_{i_k}, \boldsymbol{l}_{j_k}) - \boldsymbol{z}_k)$ is the robustified prediction error of observation $k$ obtained from the E step, and $w_{j_k}$ is the weight to estimate for landmark $l = j_k$ associated with the $k$-th observation. We equate the derivative of the objective function with respect to $w_l$ to zero, and maximize the log likelihood, then for each $w_l$ we get
\begin{equation}
\begin{aligned}
w_l = 1 - \frac{1}{\lambda} \sum_{k \in K_l}\tilde{\boldsymbol{\mu}}^T_k\boldsymbol{\Sigma}_k^{-1}\tilde{\boldsymbol{\mu}}_k
\end{aligned}
\label{eq:wk}
\end{equation}
where $K_l$ is the set of measurements of landmark $l$, and $\lambda$ is an assigned constant parameter to trade off the penalty. Larger $\lambda$ will penalize more against the number of landmarks being mobile $w_k = 0$ for any $k$.

\subsection{Graph SLAM Optimization}

In the \textbf{E step}, we use the estimated latent parameters to obtain minimum variance results with graph optimization methods. We employ the standard approach of graph optimization as in \cite{g2o}, with our augmentation to the objective by introducing landmark mobility indicators $w_{j_k}$ and observation robust kernel $v_k$. Specifically, we want to compute the maximum likelihood estimate of the robust objective
\begin{equation}
\begin{aligned}
X^*, L^* = \operatorname*{arg\,max}_{X, L} & \{ -\log p(X, L, U, Z, W) \}\\
=\operatorname*{arg\,max}_{X, L} & \{ \sum_{i=1}^M||f_i(\boldsymbol{x}_{i-1}, \boldsymbol{u}_i) - \boldsymbol{x}_i||^2_{\boldsymbol{\Gamma}_i} \\
&+ \sum_{k=1}^K w_{j_k}|| v_k (h_k(\boldsymbol{x}_{i_k}, \boldsymbol{l}_{j_k}) - \boldsymbol{z}_k)||^2_{\boldsymbol{\Sigma}_k} \\ 
&+ \sum_{k=1}^K ||1 - v_k||^2_{\boldsymbol{\Xi}_k} \}
\end{aligned}
\label{eq:MAP}
\end{equation}
where the $||.||_{\boldsymbol{\Sigma}}$ term denotes the Mahalanobis distance with covariance $\boldsymbol{\Sigma}$. The penalty term $|| 1 - v_k||^2_{\boldsymbol{\Xi}_k}$ here is the switching prior introduced in \cite{Switchable12}. Note that in this step, $\boldsymbol{w}$ is fixed and the penalty term with respect to $w_k$ in the objective for estimating $\boldsymbol{w}$ becomes a constant, thus it does not appear in the objective function.

Here we apply the Dynamic Covariance Scaling\cite{DCS} kernel $v_k$ to each individual observation $k$. The factor $v_k$ for observation $k$ is given as:

\begin{equation}
\begin{aligned}
v_k = \min \left\{ 1, \frac{2\Phi}{\Phi + w_{j_k}\boldsymbol{\mu}_k^T \boldsymbol{\Sigma}_k^{-1} \boldsymbol{\mu}_k}\right\}
\end{aligned}
\label{eq:DCS}
\end{equation}

where $\boldsymbol{\mu}_k = h_k(\boldsymbol{x}_{i_k}, \boldsymbol{l}_{j_k}) - \boldsymbol{z}_k$ is the original prediction error of observation $k$. The DCS kernel is shown to result in an upper bound specified by $\Phi$ for the second part of the objective function. By specifying the upper bound $\Phi$ for all robust edges, $v$ dynamically scales the information matrices of all edges each iteration within the graph optimization process, and replaces the covariances of outliers with large ones making it near uniform. $\Phi$ is chosen as 1 in our implementation as suggested by its author. 

With some derivation %\footnote{See Appendix section \ref{appendix:leastsquare} for detail.}
(Appendix section), the optimization problem can be formed as a standard least-squares problem:
%resolved\cj{why the subscript covariance $_2$? xlz: removed $_2$, this is just plain L2-norm}

\begin{equation}
\boldsymbol{\delta}^* = \operatorname*{arg\,max}_{\boldsymbol{\delta}}||\boldsymbol{A}\boldsymbol{\delta} - \boldsymbol{b}||^2
\label{eq:optimization}
\end{equation}


The algorithm, while reliable as shown in experiments in \cite{haehnel03iros}, is possible to have variants modified for real-time updates. In our current implementation we perform batch optimization. We need to rerun the EM algorithm if new measurements are observed. Incremental implementation of the framework is subject for future work.

\subsection{Incremental Optimization}
We introduce the theoretical basis for an incremental implementation of the EM algorithm for the problem. As suggested in \cite{neal1998EM}, if the joint probability is fully factorized with regards to the examples, as is in our case, we can use the following algorithm for update in the E and M step while preserving the correctness:

\paragraph{E step} 
In equation \ref{eq:MAP}, if we have one new observation $\boldsymbol{z}_{K+1}$ at time $K+1$, then

\begin{equation}
\begin{aligned}
\boldsymbol{x}_{i_{K+1}}^*, \boldsymbol{l}_{j_{K+1}}^*  
&= \operatorname*{arg\,max}_{ \boldsymbol{x}_{i_{K+1}}, \boldsymbol{l}_{j_{K+1}}} \{ 
\sum_{i}||f_i(\boldsymbol{x}_{i-1}, \boldsymbol{u}_i) - \boldsymbol{x}_i)||^2_{\boldsymbol{\Gamma}_i} \\
&\hspace{0.5cm}+ \sum_{k=1}^{K+1} w_{j_k}||v_k(h_k(\boldsymbol{x}_{i_k}, \boldsymbol{l}_{j_k}) - \boldsymbol{z}_k)||^2_{\boldsymbol{\Sigma}_k} \\ 
&\hspace{0.5cm}+ \sum_{k=1}^{K+1}||1-v_k||^2_{\boldsymbol{\Xi}_k} \}
%&= \operatorname*{arg\,max}_{ x_{i_{K+1}}, l_{j_{K+1}}} \{ 
%\sum_{i}||f_i(x_{i-1}, u_i) - x_i)||^2_{\Gamma_i} \\
%&+ \sum_{k=1}^{K+1} w_{j_k}||v_k(h_k(x_{i_k}, l_{j_k}) - z_k)||^2_{\Sigma_k} \\
%&+ \sum_{k=1}^{K+1}||1-v_k||^2_{\Xi_k} \}
\end{aligned}
\label{eq:facMAP}
\end{equation}

and equation \ref{eq:facMAP} can also be written in the form of \ref{eq:optimization}, but with less parameters. So, the incremental E step becomes
\begin{itemize}
\item Choose one observation term $k$ to be updated, such as $k = K+1$
\item Set $\boldsymbol{x}_{i_p}^{(t)} = \boldsymbol{x}_{i_p}^{(t-1)}, \boldsymbol{l}_{j_p}^{(t)} = \boldsymbol{l}_{j_p}^{(t-1)}$ for $p \neq k$
\item Set $\boldsymbol{x}_{i_k}, \boldsymbol{l}_{j_k}$ according to equation \ref{eq:MAP} in equation \ref{eq:optimization}'s form.
\end{itemize}
\paragraph{M step} The same step as introduced in section \ref{sec:traditionalEM}, using the derivation in equation \ref{eq:wk}.

With this incremental EM algorithm, the E step can be much faster since the optimization problem has less parameters. Also, after several iterations, we may use the model to update the parameters by adding more observations, without the need to run the EM algorithm on all the observations again.
